---
title: "Logistic Regression with R"
author: "Charlotte_k"
date: "1/15/2022"
output: html_document
---

#### **0. Logistic Regression Intro.**
- Similar to a linear regression model **where the dependent variable is categorical** rather than numeric (continuous).
- This note focus on **binary** dependent variable (0 or 1). For example, pass/fail, alive/dead, win/lose...etc.
- Approach: the binary logistic model is used to **estimate the probability** (based on odds) of a binary response.



#### **1. Load Chrun data, take a look at the file and see summary**

```{r}
churndata = read.table('/Users/rouhsin_charlotte/Downloads/6312:13_Statistics data/Churndata.dat', header = TRUE)
head(churndata)
```

```{r}
summary(churndata)
```

#### **2. Build Logistic Regression Model (Choosing Logistic Model)**
- There are other well-defined nonlinear models like Angular, Gompertz, Burr, Urban, **Logistics, and Probit.**
- We are getting **Ln(Odds(DropOut)) = b0 + b1*Age**
```{r}
churn.logit = glm(Dropout~Age, data = churndata, family = binomial(link = 'logit'))
summary(churn.logit)
```

#### **3. Plot the Model**
```{r}
AgeVals = seq(0,80,1)
NewData = data.frame(AgeVals)
NewData["PredVal"] = predict(churn.logit, list(Age = NewData$AgeVals), type = "link")
NewData["PredProb"] = exp(NewData$PredVal)/(1+exp(NewData$PredVal))
NewData["PredProb2"] = predict(churn.logit, list(Age = NewData$AgeVals), type = "response")
print(head(NewData))
```

```{r}
plot(NewData$AgeVals, NewData$PredProb, pch = 16, xlab = "Age", ylab = "Predicted Probability")
```

#### **4. Interpretation of B0 and B1**
- `exp(b1)` represents the **expected amount by which odds are multiplied** when the independent variable is increased by 1 unit.
- `(exp(b1)-1)x100` represents the **expected percentage change in the odds** associated with a 1 unit increase in the independent variable.
- `exp(b0)` represents the **expected odds when the independent variable is equal to 0**. In the current context, it's meaningless. 

#### **5. Hypothesis Test in Logistic Regression**
H0: B1  = 0 The best-fitting logistic curve in population is a horizontal straight line.
H1: B1 != 0 The best-fitting logistic curve in population is NOT a horizontal straight line.

#### **6. How well is your prediction model?**
- There's no R^2 statistic with logistic regression.
- Pseudo R^2, in this case, serve a similar purpose: McFadden's R2

##### **a. McFadden's R2**
- Ranging from 0 to just under 1, with values closer to 1 indicating the model has more predictive power.
- Values **greater than 0.4** are good.
```{r}
library(pscl)
pR2(churn.logit)
```

##### **b. Receiver Operating Characteristic (ROC) Curves and AUROC**
- ROC measures classification performance.

```{r}
library(pROC)
ROC.curve = roc(Dropout~Age, data = churndata)
plot(ROC.curve, col = "red")
```

- Area under the ROC curve ranges from 0.5 ro 1.
- Values above 0.8 indicate that  the model does a good job in **discriminating between the two categories of the outcome variable**.
```{r}
# Area under the curve
auc(ROC.curve)
```
